taxize - taxonomic search and retrieval in R

### 2013-06-10 inst/doc/taxize_withcode_appB.Rnw
fixed typos

To analyse trait-composition abundance data must be matched with trait databases like \citet{usseglio-polatera_biological_2000}. However these two datatables may contain species information on different taxonomic levels and perhabs data must be aggregated to a joint taxomic level.

@@

The next step is to search for species were we have to aggregate tait-data, since our abundance data is on a lower taxonomic level.
We are walking the taxomomic latter for the species in our trait-data upwards and search for matches with out abundance data. Since we'll have many taxa in the trait-data belonging to one taxon, we'll take the median modality scores as an approximation. Of course also other methods may be used here, e.g. weighting by genetic distance.

>>>>

To analyse trait-composition abundance data must be matched with trait databases like \citet{usseglio-polatera_biological_2000}. However these two datatables may contain species information on different taxonomic levels and perhaps data must be aggregated to a joint taxonomic level.

@@

The next step is to search for species were we have to aggregate trait-data, since our abundance data is on a lower taxonomic level.
We are walking the taxonomic latter for the species in our trait-data upwards and search for matches with out abundance data. Since we'll have many taxa in the trait-data belonging to one taxon, we'll take the median modality scores as an approximation. Of course also other methods may be used here, e.g. weighting by genetic distance.
